### 2017-01-17 R/tutorial.Rmd
Update to tutorial

```{r figwidth, eval = TRUE,  warning = FALSE, message = FALSE, echo = FALSE}
fig.width <- 6
phi <- (1+sqrt(5))/2 # the golden ratio ;)
```

First load the package from Github.  To do this you need the package
devtools.

```{r, libs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
options(repos='http://cran.rstudio.com/')
install.packages("devtools")
```

Now load the package and install ITHIM.

```{r libs2, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
library("devtools")
install_github(repo = "syounkin/ITHIM")
library("ITHIM")
```

Now that ITHIM is installed and loaded the first step is to create the
baseline model.  To do so, using defaults built into the package, use
createITHIM as follows.

@@

@@

```{r parameters, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
names(ITHIM.baseline$parameters)
```

@@

Now to create the scenario we need only change one parameter.
Parameters may be changed with updateITHIM.  First we change the mean
walking time muwt to 120 minutes.

```{r scenario, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
ITHIM.scenario <- updateITHIM(ITHIM.baseline, "muwt", 120)
```
Now to run the comparative risk assesment use compareModels.
```{r CRA, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
comparativeRisk <- compareModels(ITHIM.baseline, ITHIM.scenario)
```

>>>>

## ITHIM Tutorial

### Installing the package

```{r figwidth, eval = TRUE,  warning = FALSE, message = FALSE, echo = FALSE}
fig.width <- 6
phi <- (1+sqrt(5))/2 # the golden ratio ;)
options(repos='http://cran.rstudio.com/')
```

First load the package from Github.  To do this you need the package
_devtools_.

```{r, libs, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
install.packages("devtools")
library("devtools")
```

Now use _install\_github_ to install _ITHIM_ and be sure to load it with _library_.

```{r libs2, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
install_github(repo = "syounkin/ITHIM", ref = "devel")
library("ITHIM")
```

### Step-by-step

Now that ITHIM is installed and loaded the first step is to create an
ITHIM object that represents the baseline vision.

To do so we may create the default ITHIM object using _createITHIM_.
createITHIM as follows.

@@

An ITHIM object is an R object that conatins, among other things, a
set of parameters that define the model.  To view these parameters we
may use _getParameterSet_.

```{r class, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
getParameterSet(ITHIM.baseline)
```

@@

@@

Now to create the scenario we need only change one parameter.
Parameters may be changed with _update_.  First we change the mean
walking time muwt to 120 minutes.

```{r scenario, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
ITHIM.scenario <- update(ITHIM.baseline, list(muwt =120))
```
Now to run the comparative risk assesment use compareModels.
```{r CRA, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
comparativeRisk <- compareModels(ITHIM.baseline, ITHIM.scenario)
```
